---
title       : "Shiny App: Predicting Outcomes with MTCars data and a Linear Best-Fit"
subtitle    : Quick and Easy Data Exploration
author      : Ethan
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz]        # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Summary of the App

The App allows for 

1. Visually exploration of all the variables in the MTCars dataset,
2. Linear regression is performed on selected pairs of data, and
3. Predictions can be performed on user chosen X-values!

The MTCars dataset

1.  Includes 32 automobiles from 1974 Motor Trend US Magazine,
2.  Includes 11 variables, which are Miles/(US) gallon, Number of cylinders,
Displacement (cu.in.), Gross horsepower, Rear axle ratio, Weight (lb/1000),
1/4 mile time, V/S, Transmission type, Number of forward gears,
Number of carburetors

--- 

## Example Plot

Plot MPG versus weight and predict the MPG of the average car that has a weight of 2000 lbs.
```{r,Echo=FALSE,results='hide',fig.height=4,fig.width=6}
library(ggplot2)
p   <- ggplot(mtcars,aes(x=wt,y=mpg))+geom_point()+xlab('MPG')+ylab('Weight(lb/1000)')                     
fit <- lm(mpg~wt,data = mtcars); b<-fit[[1]][1]; m<-fit[[1]][2]
p   <- p + geom_abline(intercept = b, slope = m ); 
p + geom_point(data=data.frame(wt=2,mpg=(m*2+b)),aes(x=wt,y=mpg),col="red",size=5)
```        

--- 

## Example Plot, continued

```{r}
y.pred <- (m*2+b)
```
The linear fit yields a slope of `r round(m,1)` and a y-intercept of `r round(b,1)`.  The predicted MPG of a car weighing 2000 lbs is `r round(y.pred,1)` mpg.  These values get displayed above the plot in the App.  

That's roughly it.  Its easy to quickly take a look at a lot of different relations.  One should keep in mind 

* That linear fits should not be extended past the data, and 
* This is not a fully representative database of all automobiles.  



--- &radio

## Review Question

Is this an amazing app and Slidify presentation describing it?

1.  Yes, Absolutely!
2.  _Well its not bad, and its pretty easy to use._
3.  Its terrible, boring and totally unoriginal.

*** .hint 

Come on, its not terrible.

*** .explanation 

Its not bad, but its not really amazing because it really was kind of easy.  But maybe it was a bit creative for the given the assignment.  

